Model-based variable selection for regression with highly correlated variables.

### 2014-04-28 www/article13.tex
up
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@558 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\begin{table}[h!]
\centering
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
$n$ & $p_r$& $P(S)$ &indicator &LASSO  &    \textsc{CorReg} $\hat S$& \textsc{CorReg} $S$\\ 
\hline %nonlin0.5global30p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_55_33.csv
30 & 0 & U&MSE (sd) & 996.06 (323.7) & 1100.17 (391.4) & 1501.25 (905.9) \\
& & &cpl (sd) & 17.66 (5.4) & 14.7 (4.7) & 11.97 (4.9) \\
 &  &HU &MSE (sd) & 996.06 (323.7) & 1094.5 (621.8) & 1501.25 (905.9) \\
& & & cpl (sd) & 17.66 (5.4) & 16.98 (4.8) & 11.97 (4.9) \\ 
\hline
\end{tabular} 
\caption{ $\boldsymbol{Y}$ depends on all variables in $\boldsymbol{X}$. \textsc{CorReg} is not too far from LASSO even if it stays behind. } \label{resYnonlin}
\end{table}

>>>>

\begin{table}[h!]
\centering
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
$n$ & $p_r$& $P(S)$ &indicator &LASSO  &    \textsc{CorReg} $\hat S$& \textsc{CorReg} $S$\\ 
\hline %nonlin0.5global30p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_55_33.csv
30 & 16 & U&MSE (sd) & 996.06 (323.7) & 1100.17 (391.4) & 1501.25 (905.9) \\
& & &cpl (sd) & 17.66 (5.4) & 14.7 (4.7) & 11.97 (4.9) \\
 &  &HU &MSE (sd) & 996.06 (323.7) & 1094.5 (621.8) & 1501.25 (905.9) \\
& & & cpl (sd) & 17.66 (5.4) & 16.98 (4.8) & 11.97 (4.9) \\ 
\hline
\end{tabular} 
\caption{ $\boldsymbol{Y}$ depends on all variables in $\boldsymbol{X}$. \textsc{CorReg} is not too far from LASSO even if it stays behind. } \label{resYnonlin}
\end{table}
